\begin{thebibliography}{99}\addcontentsline{toc}{chapter}{Bibliography}

\bibliographystyle{plain}

% 2.1 public private encryption

\bibitem{rsa-patent}
Rivest, R.L. and Shamir, A. and Adleman, L.M. US Patent 4,405,829 issued in 1983

\bibitem{ceasar-cypher}
Cipher, C., \& Cipher, M. (2004). Introduction to cryptography. EEC, 484, 584.


\bibitem{rsa-paper-explanation}
Calderbank, M. (2007). The RSA Cryptosystem: History, Algorithm, Primes.

% 2.2 Blockchain

\bibitem{blockchain-multiple-definitions}
Bischoff, P. (2017). What is Blockchain? 10 experts attempt to explain it in 150 words or less. Comparitech. Retrieved 20 July 2017, from https://www.comparitech.com/blog/information-security/what-is-blockchain-experts-explain/

\bibitem{antonopoulos:2014}
{\sc Antonopoulos, A. M.} (2014).
Mastering Bitcoin.
{\em} Sebastopol, CA.

\bibitem{data-structure}
Rouse, M. (February 2006). What is data structure? - Definition from WhatIs.com. SearchSQLServer. Retrieved 20 July 2017, from http://searchsqlserver.techtarget.com/definition/data-structure

\bibitem{abelson:1996}
{\sc Abelson, H. et al.} (1996).
Structure and Interpretation of Computer Programs.
MIT Press.

\bibitem{bitfury-pos-vs-pow}
Bitfury Group (2015). Proof of Stake vs Proof of Work

\bibitem{general-market-cap}
CryptoCurrency Market Capitalizations. (2017). Coinmarketcap.com. Retrieved 20 July 2017, from https://coinmarketcap.com/currencies/

\bibitem{proof-of-whatever}
Alternatives for Proof of Work, Part 2: Proof of Activity, Proof of Burn, Proof of Capacity, and Byzantine Generals — Bytecoin Blog. (2017). Bytecoin: private secure financial system. Retrieved 19 July 2017, from https://bytecoin.org/blog/proof-of-activity-proof-of-burn-proof-of-capacity/

\bibitem{bitfury-permissioned}
Bitfury Group (2015). Public versus Private blockchains. Part 1: Permissioned Blockchains.

\bibitem{man-in-the-middle}
Desmedt, Y. (2011). Man-in-the-middle attack. In Encyclopedia of cryptography and security (pp. 759-759). Springer US.

\bibitem{bitcoin-paper}
Nakamoto, S. (2008). Bitcoin: A peer-to-peer electronic cash system.

\bibitem{bitcoin-market-cap}
Bitcoin (BTC) price, charts, market cap, and other metrics | CoinMarketCap. (n.d.). Retrieved July 19, 2017, from https://coinmarketcap.com/currencies/bitcoin

\bibitem{bitcoin-civil-war}
Chen, L. Y., \& Nakamura, Y. (2017, July 10). Bitcoin Is Having a Civil War Right as It Enters a Critical Month. Retrieved July 19, 2017, from https://www.bloomberg.com/news/articles/2017-07-10/bitcoin-risks-splintering-as-civil-war-enters-critical-month

\bibitem{bitcoin-hash-rate}
Hash Rate - Blockchain. (n.d.). Retrieved July 19, 2017, from https://blockchain.info/charts/hash-rate

\bibitem{quantum-newsweek}
Bauer, M. R. (2017, April 14). Quantum Computing is going commercial with the potential to disrupt everything. Retrieved July 19, 2017, from http://www.newsweek.com/2017/04/21/quantum-computing-ibm-580751.html

\bibitem{namecoin-whitepaper}
Loibl, A. (2014). Namecoin. namecoin. info.

\bibitem{ethereum-pos-faq}
Buterin, V. et al. (2017). Proof of Stake FAQ. URL https://github.com/ethereum/wiki/wiki/Proof-of-Stake-FAQ

\bibitem{ethereum-whitepaper}
Buterin, V. (2013). Ethereum white paper.

\bibitem{definition-turing-completeness}
Kepser, S. (2004, August). A Simple Proof for the Turing-Completeness of XSLT and XQuery. In Extreme Markup Languages®.
Chicago 

% 2.3 Distributed databases

\bibitem{baran-distributed-communications}
Baran, P. (1964). On distributed communications networks. IEEE transactions on Communications Systems, 12(1), 1-9.

\bibitem{brewers-theorem-paper}
Fox, A., \& Brewer, E. A. (1999). Harvest, yield, and scalable tolerant systems. In Hot Topics in Operating Systems, 1999. Proceedings of the Seventh Workshop on (pp. 174-178). IEEE.

\bibitem{gilbert-lynch-cap-proof}
Gilbert, S., \& Lynch, N. (2002). Brewer's conjecture and the feasibility of consistent, available, partition-tolerant web services. Acm Sigact News, 33(2), 51-59.

\bibitem{git-manual-book}
Chacon, S., \& Straub, B. (2014). Pro git. Apress.

\bibitem{change-author-commit}
How can I change the author (name / email) of a commit? (2017). Git-tower.com. Retrieved 21 July 2017, from https://www.git-tower.com/learn/git/faq/change-author-name-email

\bibitem{github-pr}
About pull requests - User Documentation . (2017). Help.github.com. Retrieved 21 July 2017, from https://help.github.com/articles/about-pull-requests/

\bibitem{bittorrent-explanation}
Cohen, B. (2003, June). Incentives build robustness in BitTorrent. In Workshop on Economics of Peer-to-Peer systems (Vol. 6, pp. 68-72).

\bibitem{bittorrent-norm}
Andersson, J. (2009). For the good of the net: The Pirate Bay as a strategic sovereign. Culture Machine, 10.
Chicago 

\bibitem{blockchain-cap}
Goland, Y. Y. (March 8, 2017). The block chain and the CAP Theorem. Retrieved 21 July 2017, from http://www.goland.org/blockchain\_and\_cap

\bibitem{hashrate-distribution}
Hashrate Distribution. (2017). Blockchain.info. Retrieved 21 July 2017, from https://blockchain.info/pools

\bibitem{bitcoin-confirmation-amount}
Confirmation - Bitcoin Wiki. (2017). En.bitcoin.it. Retrieved 21 July 2017, from https://en.bitcoin.it/wiki/Confirmation

\bibitem{confirmation-safety}
Gornick, S. (March 13, 2013). How many confirmations do I need to ensure a transaction is successful?. Bitcoin.stackexchange.com. Retrieved 21 July 2017, from https://bitcoin.stackexchange.com/a/8373/47645

\bibitem{blockchain-scalability}
James-Lubin, K. (2015). Blockchain scalability. O'Reilly Media. Retrieved 21 July 2017, from https://www.oreilly.com/ideas/blockchain-scalability

\bibitem{ethereum-block-time}
Ethereum / Ether (ETH) statistics - Price, Blocks Count, Difficulty, Hashrate, Value. (2017). Bitinfocharts.com. Retrieved 21 July 2017, from https://bitinfocharts.com/ethereum/

\bibitem{openbazaar-faq}
FAQ - OpenBazaar Docs. (2017). Docs.openbazaar.org. Retrieved 21 July 2017, from https://docs.openbazaar.org/09.-Frequently-Asked-Questions/

% 3 aim of research
\bibitem{dropbox-sharing}
Shared folders: Give people edit access to your files. (2017). Dropbox.com. Retrieved 22 July 2017, from https://www.dropbox.com/help/files-folders/share-with-others

% 4.1 storing on bitcoin
\bibitem{bitcoin-transaction-fee}
Bitcoin Fees for Transactions | bitcoinfees.21.co. (2017). Bitcoinfees.21.co. Retrieved 22 July 2017, from https://bitcoinfees.21.co/


\end{thebibliography}
