\chapter{Conclusion}

Throughout this paper, it has become clear technology provides several alternatives to trusted third parties, at least in the context of collaborative databases. 

In  private environments, central storage providers and central interaction management providers can be replaced by blockchains. In the public environment, privileged professions such as notaries can be replaced by the more secure alternative of public key encryption and blockchains.

I think governments could largely reduce the amount of signature disputes by incorporating blockchains into the law. Although this paper specifically focused on testaments, a similar case could be made for other contracts. 

If the government does move to blockchains, several aspects have to be taken into account concerning which blockchains should be eligible. I am convinced the law should not limit itself to one single blockchain, but should rather put requirements on which public blockchains could be used: which consensus algorithm should be used, what is the minimum hashing power the blockchain should possess and what is the maximum centralization of the hashing power. 

Personally, I am convinced only proof of work has currently proven to be extremely secure. Concerning minimum hashing power, I would recommend making the law time agnostic by defining the minimum hashing power as a percentage of the estimated total computing power currently available in the world. Concerning centralization, I would recommend putting maximum cumulative shares on the largest miners. For example, the largest miner should not own more than 30\% of total hashing power, the largest two miners should not own more than 40\% combined and the largest three miners should not control more than 50\%. 

But even without laws specifically mentioning blockchain, I think blockchain verified testaments (and contracts) are already more secure. As mentioned before, a notary is not required for a Belgian testament to be valid. It is therefore only a matter of time before a case is brought before a court concerning which testament is valid: a digitally signed, blockchain verified document or a notary witnessed one. This will set an important precedent for the future, probably forcing the legislative branch to incorporate blockchains into the laws.


Concerning this specific thesis, it is unfortunate I could no dive deeper into the technical aspects of distributed cloud storage. Cutting edge innovation seems to be happening in this space right now. For example Filecoin, an alternative to Siacoin or Storj, published their updated whitepaper on August 4, 2017, only two weeks before the deadline of the thesis. Unfortunately, I did not have enough time to incorporate proper review of their proposal. Furthermore, the ambition of projects such as IPFS and Maidsafe are really impressive. I am sure it would be interesting to compare all the different projects both technically and from a business case point of view. 